Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2021-01-11 vesicle_code/docs/permeableVes/main.tex
added in shear and stenosis tensions
adding tension plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Vesicle Tensions}
\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} Tension of vesicles in
  relaxation.}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/stenosisTensions.tikz}
  \else
    \includegraphics{figures/stenosisTensions.pdf}
  \fi
  \caption{\label{fig:stenosisTensions} Tension of vesicles in
  stenosis.}
\end{figure*}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Vesicle Tensions}
\begin{figure*}[htp]
  \centering
  \ifTikz
    \input{figures/relaxationTensions.tikz}
  \else
    \includegraphics{figures/relaxationTensions.pdf}
  \fi
  \caption{\label{fig:relaxationTensions} Tension of vesicles in
  relaxation.}
  \todo[inline]{Redo using cline}
\end{figure*}

\begin{figure*}[hbp]
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
    };
    \node at (-8.54,0.6) {(a)};
    \node at (-6.00,0.6) {(b)};
    \node at (-3.46,0.6) {(c)};
    \node at (-0.92,0.6) {(d)};
    \node at (+1.60,0.6) {(e)};
    \node at (+4.16,0.6) {(f)};
    \node at (+6.70,0.6) {(g)};
  \end{tikzpicture}
%  \includegraphics[width=\textwidth]{figures/shearTensions.pdf}
  \caption{\label{fig:shearTensions} Tension of vesicles in
  shear flow. The semi-permeability constant is $\beta = 10^{-4}$ for
  all these cases, and the elastic capillary number ranges from
  $10^{-1}$ to $10^{2}$ as in Figure~\ref{fig:shearComposite}.}
\end{figure*}

\begin{figure*}[hbp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/parabolicTensions.pdf}
    };
    \node at (-8.2,1.5) {(a)};
    \node at (-3.8,1.5) {(b)};
    \node at (+0.6,1.5) {(c)};
    \node at (+5.0,1.5) {(d)};
  \end{tikzpicture}
  \caption{\label{fig:parabolicTensions} The steady state tension
  profile of a semipermeable vesicle with $\beta=10^{-3}$ in a parabolic
  flow (see Figure~\ref{fig:parabolicComposite}). The flow velocities
  are (a) 200$\mu$m/s, (b) 400$\mu$m/s, (c) 600$\mu$m/s, and (d)
  800$\mu$m/s.}
\end{figure*}

\begin{figure*}[htp]
  \centering
  \begin{tikzpicture}[scale=1]
    \node[inner sep=0pt] at (0,0) {
    \includegraphics[width=\textwidth]{figures/stenosisTensions.pdf}
    };
    \node at (-8.6,0.7) {(a)};
    \node at (-1.6,0.7) {(b)};
  \end{tikzpicture}
  \caption{\label{fig:stenosisTensions} Tension of vesicles in
  stenosis.}
\end{figure*}
